### 2023-03-30 application.tex
details

@@

\subsection{Vector Addition System with States}

>>>>

\subsection{VASS, 2-VASS, semilinear VASS, Lossy Channel Systems, Integer et Continuous VASS, Regular Channel Systems}

\begin{theorem}{}
Resilience is decidable for semilinear VASS, LCM, Integer et Continuous VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

se déduit du papier Schnoebelen RP 2010, page 8

\begin{theorem}{}
Resilience is decidable for Regular Channel Systems when $\Safe$ and $\Bad$ are regular languages.
\end{theorem}

open for VASS ???

@@

%
%
%\subsection{Vector Addition System with States or PN}
%
%\textcolor{red}{Should be defined in a later 'application section' once we start writing any proof, for now I leave it there} 
%
